### 2015-11-20 section/3_redundancy.tex
test

After identifying \textit{inputs} using static analysis, 
\Tool then instruments the program to record \textit{inputs} values at run time.
%Specifically, we will assign
%a unique ID for each source instruction, and a pair of $<InstID, Value>$
%will be recorded at run time with the execution of a source instruction.
The run-time trace will also include delimiters and meta information that allows
trace analysis to differentiate values recorded from different instructions, 
loop
iterations, loop instances, and so on.
%TODO
%All values defined outside the loop is recorded in block O. 
%We record a delimiter, loop instance number and values defined in previous iterations in block H1'.
%Since we only consider redundant iterations from the same loop instance,  
%we do not record values defined outside the loop for cross-iteration redundancy.

Once the trace under problematic workload is collected either during
off-line debugging or during production runs, 
\Tool will process the trace and decide
whether the loops under study contain cross-iteration redundancy or 
cross-loop redundancy. We will first present our high-level algorithms, followed
by the exact implementation in our prototype.

@@

The key of this implementation is
to judge whether two dynamic loop instances $l_1$ and $l_2$ 
are redundant or not.
The challenge is that $l_1$ and $l_2$ may have executed different numbers of
iterations; in different iterations, different sets of source instructions
may have executed. Therefore, we cannot simply chain values from different
input instructions and iterations together and compare two data sequences.
Instead, we decide to check the redundancy for each source instruction across
$l_1$ and $l_2$ first, and then use the average \textit{redundancy rate} of
all source instructions as the \textit{cross-loop redundancy rate} between
$l_1$ and $l_2$.

We calculate the redundancy for one source instruction $I$ by normalizing the
edit-distance between the two sequences of values returned by $I$ in the two
loop instances. The exact formula is the following:

@@

Recording values returned by every source instruction would lead to 
huge run-time overhead. To lower the overhead,
we use random sampling to reduce the number of instructions that we
track at run time. Due to the repetitive nature of performance bugs,
we will still be able to recognize redundant 
computation as long as the sampling rate is not too sparse, which
we will evaluate
in Section \ref{sec:experiment}. 
Our sampling scheme requires almost no changes to our redundancy 
identification algorithm discussed in Section \ref{sec:cal}.

%Another observation, which can also be demonstrated by examples shown in Figure~\ref{fig:Mozilla477564} and Figure~\ref{fig:Apache34464}, 
%is that two consecutive loop instances are good targets to compare.

>>>>

After identifying \textit{inputs} using static analysis, 
\Tool then instruments the program to record \textit{inputs} values at run time.
%Specifically, we will assign
%a unique ID for each source instruction, and a pair of $<InstID, Value>$
%will be recorded at run time with the execution of a source instruction.
The run-time trace will also include delimiters and meta information that allows
trace analysis to differentiate values recorded from different instructions, 
loop
iterations, loop instances, and so on.
%TODO
%All values defined outside the loop is recorded in block O. 
%We record a delimiter, loop instance number and values defined in previous iterations in block H1'.
%Since we only consider redundant iterations from the same loop instance,  
%we do not record values defined outside the loop for cross-iteration redundancy. 
Once the trace under problematic workload is collected either during
off-line debugging or production runs, 
\Tool will process the trace and decide
whether the loops under study contain cross-iteration or 
cross-loop redundancy. We will first present our high-level algorithms, followed
by the exact implementation in our prototype.

@@

The key of this implementation is
to judge whether two dynamic loop instances $l_1$ and $l_2$ 
are redundant or not.
The challenge is that $l_1$ and $l_2$ may have executed different numbers of
iterations; in different iterations, different sets of input instructions
may have executed. Therefore, we cannot simply chain values from different
input instructions and iterations together and compare two data sequences.
Instead, we decide to check the redundancy for each input instruction across
$l_1$ and $l_2$ first, and then use the average \textit{redundancy rate} of
all input instructions as the \textit{cross-loop redundancy rate} between
$l_1$ and $l_2$.

We calculate the redundancy for one input instruction $I$ by normalizing the
edit-distance between the two sequences of values returned by $I$ in the two
loop instances. The exact formula is the following:

@@

Recording values returned by every input instruction would lead to 
huge run-time overhead.
\Tool uses random sampling to reduce this overhead, which 
requires almost no changes to our redundancy 
identification algorithm discussed in Section \ref{sec:cal}.

Note that, \Tool leverages sampling to gain performance with \textbf{no}
sacrifice to diagnosis latency or quality, which is
\textbf{different} from traditional sampling techniques
for diagnosing correctness failures \cite{liblit03,liblit05}, where
many more failure runs and hence longer diagnosis latency
are needed to compensate for the performance gain.
Performance bugs have a unique repetitive nature:
a loop can cause a severe performance problem only when it 
contains many redundant iterations/instances.
Therefore, we can still recognize redundant behavior in just
\textbf{one} failure run, 
as long as the sampling is not insanely sparse
(Section \ref{sec:experiment}). 
%Another observation, which can also be demonstrated by examples shown in Figure~\ref{fig:Mozilla477564} and Figure~\ref{fig:Apache34464}, 
%is that two consecutive loop instances are good targets to compare.
